\chapter{參考文獻}
\begin{itemize}
\item 郭亭佑. (2021). 透過文字探勘預測台股報酬. \textit{政治大學金融學系學位論文}
\item Blei, D. M., Ng, A. Y., and Jordan, M. I. (2003). Latent dirichlet allocation. \textit{Journal of Machine Learning Research, 3,}993-1022
\item Chen, Y. L, Dai, C. S and Ing, C. K (2019). High-dimensional model selection via Chebyshev greedy algorithms. Working paper.
\item Fan, J., Xue, L., and Zhou, Y. (2021). How much can machines learn finance from Chinese text data?. Working Paper.
\item Gentzkow, M., Kelly, B., and Taddy, M. (2019). Text as data. \textit{Journal of Economic Literature, 57 }(3), 535-74.
\item Henry, E. (2008). Are investors influenced by how earnings press releases are written?. \textit{The Journal of Business Communication, 45}(4), 363–407.
\item Ing, C. K., and Lai, T. L. (2011). A stepwise regression method and consistent model selection for high-dimensional sparse linear models. \textit{Statistica Sinica}, 1473-1513.
\item Jegadeesh, N., and Wu, D. (2013). Word power: A new approach for content analysis. \textit{Journal of Financial Economics, 110(3)}, 712-729.
\item Ke, Z. T., Kelly, B. T., and Xiu, D. (2019). Predicting returns with text data. Working Paper.
\item Loughran, T., and McDonald, B. (2011). When is a liability not a liability? Textual analysis,
dictionaries, and 10-Ks. \textit{Journal of Finance, 66}(1), 35-65.
\item Manela, A., and Moreira, A. (2017). News implied volatility and disaster concerns. \textit{Journal of Fi-
nancial Economics, 123(1)}, 137–162.
\item Temlyakov, V. N. (2015). Greedy approximation in convex optimization. \textit{Constructive Approxima- tion, 41}(2), 269-296.
\item Tetlock, P. C. (2007). Giving content to investor sentiment: The role of media in the stock market. \textit{The Journal of Finance, 62}(3), 1139-1168.
\item Tibshirani, R. (1996). Regression shrinkage and selection via the lasso. \textit{Journal of the Royal Statistical Society: Series B (Methodological), 58}(1), 267-288.
\item You, J., Zhang, B., and Zhang, L. (2018). Who captures the power of the pen?. \textit{Review of Financial Studies, 31}(1), 43–96.
\end{itemize}

































